---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oneliner

This package builds on [styler](https://github.com/r-lib/styler) by providing a 
third-party style guide that can be applied to code with styler's code 
formatters such as `style_text()`.

Let's see an example
```{r}
# remotes::install_github("lorenzwalthert/oneliner")
library(oneliner)
style_text(
  "sum <- function(x, y) {
   x + # hi
   y
  }
  1 + 1",
  style = one_line_style
)
```


The name of the style guide is self-explanatory. Put all code on one line. 
Advantages of the style guide proposed include:

* Entirely self-explanatory (probably biggest plus).
* It ends the tabs / spaces indention war in an unexpected and elegant way.
* You don't need to worry about EOL markers.
* You can easily export to csv. One command per column.
* and so on.

I am sure I have convinced you that this style guide rocks. This is for real 
programmers. All code on one line. No spaces or comments. I am serious. Use this
style guide to format your code like nerds do.
